\section{Implementation}

In this section, we wil describe our implementation of various terms 
in Kohn-Sham equations using Lagrange basis functions.
The computer program which contains our implementation can be found in public
repository: \url{https://github.com/f-fathurrahman/ffr-LFDFT}.

\subsection{Kohn-Sham equations in Lagrange basis functions representation}

Using Lagrange basis function \ref{eq:LF_p_1d} and its extension in 3d, Kohn-Sham orbitals
at point $\mathbf{r} = (x,y,z)$ can be written as
\begin{equation}
\psi_{i_{st}}(x,y,z) = \sum_{\alpha}^{N_x} \sum_{\beta}^{N_y} \sum_{\gamma}^{N_z}
C_{\alpha\beta\gamma}^{i_{st}} L_{\alpha}(x) L_{\beta}(y) L_{\gamma}(z)
\end{equation}
%
Using this expansion, kinetic operator can be written as
\begin{align}
T_{\alpha\beta\gamma}^{\alpha'\beta'\gamma'} & = -\frac{1}{2} \sum_{i_{st}} f_{i_{st}}
\Braket{ \psi_{i_{st}} | \nabla^2 | \psi_{i} } \\
& =
-\frac{1}{2}
\sum_{i_{st}} f_{i_{st}} \sum_{\alpha\alpha'} \sum_{\beta\beta'} \sum_{\gamma\gamma'}
C^{i_{st}}_{\alpha\beta\gamma} \mathbb{L}_{\alpha\beta\gamma}^{\alpha'\beta'\gamma'}
C^{i_{st}}_{\alpha'\beta'\gamma'}
\end{align}
%
were the Laplacian matrix $\mathbb{L}_{\alpha\beta\gamma}^{\alpha'\beta'\gamma'}$
has the following form:
\begin{equation}
\mathbb{L}_{\alpha\beta\gamma}^{\alpha'\beta'\gamma'} =
D^{(2)}_{\alpha\alpha'}\delta_{\beta\beta'}\delta_{\gamma\gamma'} +
D^{(2)}_{\beta\beta'}\delta_{\alpha\alpha'}\delta_{\gamma\gamma'} +
D^{(2)}_{\gamma\gamma'}\delta_{\alpha\alpha'}\delta_{\beta\beta'}
\end{equation}
%
Specifically, for periodic Lagrange basis function $D^{(2)}_{ij}$, $i, j = \alpha, \beta, \gamma$
can be written as follows.
\begin{equation}
D^{(2)}_{ij} = -\left( \frac{2\pi}{L} \right)^2 \frac{N'}{3} \left( N' + 1 \right) \delta_{ij} \\
+ \dfrac{ \left(\dfrac{2\pi}{L}\right)^2 (-1)^{i-j}\cos\left[\dfrac{\pi(i-j)}{N}\right]}
{2\sin^2\left[\dfrac{\pi(i-j)}{N}\right]}
(1-\delta_{nn'})
\label{eq:kin1d_p}
\end{equation}
where $N' = (N-1)/2$.

The matrix representation of kinetic operator is sparse.

The remaining potential terms which are local have very simple matrix form, i.e.
diagonal. The action of potential operator to Kohn-Sham orbital at point
$(r_{\alpha\beta\gamma})$ thus can be
obtained by pointwise multiplication with the potential on that point:
\begin{equation}
V_{\mathrm{KS}}(r_{\alpha\beta\gamma}) = V_{\mathrm{ion}}(r_{\alpha\beta\gamma}) +
V_{\mathrm{Ha}}(r_{\alpha\beta\gamma}) + V_{\mathrm{xc}}(r_{\alpha\beta\gamma})
\end{equation}

\subsection{Methods to solve Kohn-Sham equations}

We implement two methods to solve the Kohn-Sham equations, namely
via the self-consistent field (SCF) iterations and
direct energy minimization.

Outline of SCF iterations:
\begin{itemize}
\item Guess density $\rho(\mathbf{r})$
\item Iterate until convergence
\begin{itemize}
\item Calculate Kohn-Sham potentials $V_{\mathrm{KS}}$ and build the Kohn-Sham
Hamiltonian $H_{\mathrm{KS}}$
\item Diagonalize $H_{\mathrm{KS}}$ to obtain $\mathrm{\psi_{i_{st}}}(\mathbf{r})$
and $\epsilon_{i_{st}}$.
\item Calculate charge density and total energy. If the calculation converges
the stop the calculation, if not iterate.
\end{itemize}
\end{itemize}

Outline of direct minimization, using 
\begin{itemize}
\item Generate guess Kohn-Sham orbitals, orthonormalize if needed.
\item Calculate charge density, build Kohn-Sham potential and calculate total energy
for this
\item Iterate until convergence:
%
\begin{itemize}
%
\item Calculate Kohn-Sham electronic gradient $\mathbf{g}_{\psi}$ and the preconditioned
gradient $\mathbf{Kg}_{\psi}$ where $\mathbf{K}$ is a preconditioner.
%
\item Calculate search direction:
\begin{equation}
\beta = \dfrac{\mathbf{g}_{\psi}^{\dagger}\mathbf{Kg}_{\psi}}
{\mathbf{g}_{\psi,\mathrm{prev}}^{\dagger}\mathbf{Kg}_{\psi,\mathrm{prev}}}
\end{equation}
If $\mathbf{g}_{\psi,\mathrm{prev}}$ is not available (first iteration) then set
$\beta = 0$.
%
\item Calculate new direction:
\begin{equation}
\mathbf{d} = 
\end{equation}
\end{itemize}
%
\end{itemize}
