\documentclass[%
reprint, floatfix, amsmath, amssymb, aps]{revtex4-1}

\usepackage{graphicx}
\usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
\usepackage[utf8x]{inputenc}
\usepackage{hyperref}
\usepackage{mhchem}

\begin{document}



\title{Development of a computer program for electronic structure calculation using Lagrange basis functions}
\author{Fadjar Fathurrahman, Hermawan K. Dipojono}
\affiliation{
Department of Engineering Physics, Bandung Institute of Technology \\
Research Center for Nanoscience and Nanotechnology, Bandung Institute of Technology
}

\begin{abstract}
Electronic structure calculation is one approach that can be used to study material,
especially at nanoscale where quantum nature of electrons might play important role
to determine material properties. Among various methods for electronic structure calculation,
density functional theory (DFT) based on Kohn-Sham equations is considered to be a popular one.
In the the implementation to solve Kohn-Sham equations, single-electron wave function must be
represented as an expansion of basis functions or some discretization schemes. Several
existing computer programs for DFT calculations, such as  Quantum Espresso and Gaussian09,
expand single-electron wave function using plane wave and Gaussian functions, respectively.
Others, such as Octopus and GPAW use discretization based on finite-difference scheme.
In this article, we report our initial effort to implement a new computer program to
solve Kohn-Sham equations using expansion in Lagrange basis functions (LFs).
Use of this basis set in Kohn-Sham equation results in matrix eigenproblem which
is similar to matrix eigenproblem in finite difference schemes. Two methods to solve
Kohn-Sham equation, namely self-consistent field iterations and direct minimization,
are reported. Comparisons done with finite difference scheme implemented in Octopus
for several simple systems shows that total energy convergence with respect to the number
of grid points is better when using Lagrange basis functions.
\end{abstract}

\maketitle

\input{Intro}

\input{Theory}

\input{Implementation}

\input{Results}


\bibliography{LFDFT-v2}

\end{document}


